The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-06-10 manuscript/5pillars.Rmd
keywords added
Add reference citations for Project Jupyter

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
author: "Mark Ziemann, Samuel S. Minot, Pierre Poulain, Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: 5pillars.bib
csl: plos-computational-biology.csl
---

Mark Ziemann<sup>1*</sup>, Samuel S. Minot<sup>2</sup>, Pierre Poulain<sup>3</sup>,
Anusuiya Bora<sup>1</sup>

<details><summary>Author information (*click to expand*)</summary><p>

@@

2. Fred Hutchinson Cancer Center, Seattle, USA.

3. Université Paris Cité, CNRS, Institut Jacques Monod, Paris, France.

Correspondance: m.ziemann@deakin.edu.au

| Author | ORCID |
| --- | --- |
| Mark Ziemann | 0000-0002-7688-6974 |
| Samuel S. Minot | 0000-0003-1639-3905 |
| Pierre Poulain | 0000-0003-4177-3619 |
| Anusuiya Bora | 0009-0006-2908-1352 |

</details>
</p>
Source: https://github.com/markziemann/5pillars/blob/main/manuscript/5pillars.Rmd

## Summary

@@

@@

Around the same time, Project Jupyter was developed to provide a "notebook" type interface, incorporating
R, Python, Julia and other computer language chunks into documents @Perkel2018-rz.
The MyST{NB} (short for Markedly Structured Text notebook) is built on top of Jupyter and has some
notable advantages around flexibility of content that make it an attractive choice for executable
article authoring [@DuPre2022-bk].

@@

We are grateful to individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and
Dr Irene López Santiago (EMBL-EBI).
Special thanks to Dr Altuna Akalin (Max Delbrück Center, Germany) and
Dr Simon Tournier (Paris Cité University, France) for advice on Guix.

This research was supported by use of the Nectar Research Cloud, a collaborative Australian research
platform supported by the NCRIS-funded Australian Research Data Commons (ARDC).

>>>>

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
author: "Mark Ziemann, Pierre Poulain, Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: 5pillars.bib
csl: plos-computational-biology.csl
---

Mark Ziemann<sup>1*</sup>, Pierre Poulain<sup>2</sup>, Anusuiya Bora<sup>1</sup>

@@

2. Université Paris Cité, CNRS, Institut Jacques Monod, Paris, France.

* Correspondance: m.ziemann@deakin.edu.au

| Author | ORCID |
| --- | --- |
| Mark Ziemann | 0000-0002-7688-6974 |
| Pierre Poulain | 0000-0003-4177-3619 |
| Anusuiya Bora | 0009-0006-2908-1352 |

Source: https://github.com/markziemann/5pillars/blob/main/manuscript/5pillars.Rmd

<br>

## Abstract

@@

**Keywords:** Reproducibility; computational research; bioinformatics; research best practices.

<br>

@@

Around the same time, Project Jupyter was developed to provide a "notebook" type interface, incorporating
R, Python, Julia and other computer language chunks into documents [@kluyver2016; @granger2021; @Perkel2018-rz].
The MyST{NB} (short for Markedly Structured Text notebook) is built on top of Jupyter and has some
notable advantages around flexibility of content that make it an attractive choice for executable
article authoring [@DuPre2022-bk].

@@

We are grateful to individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and
Dr Irene López Santiago (EMBL-EBI).
Special thanks to Dr Altuna Akalin (Max Delbrück Center, Germany) and
Dr Simon Tournier (Paris Cité University, France) for advice on Guix.
We appreciate advice on Python notebooks from Samuel S. Minot (Fred Hutchinson Cancer Center).
This research was supported by use of the Nectar Research Cloud, a collaborative Australian research
platform supported by the NCRIS-funded Australian Research Data Commons (ARDC).

<br>
